Resources for Data-Driven Search-Based Software Engineering

### 2018-01-19 main.tex
Check after renaming

\usepackage{color}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{graphicx} 
\usepackage{multirow}
\usepackage{siunitx}
\usepackage{rotating}
\usepackage{eqparbox}
\usepackage{wrapfig}
\usepackage{mathtools}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{lstlinebgrd}
\usepackage{amssymb}
\usepackage{amsmath}

@@

%Conference
\acmConference[FSE'18]{Florida}{Nov 2018}{} 
\acmYear{2018}
\copyrightyear{2018}

@@

\maketitle

% \input{samplebody-conf}
\section{Introduction}
The Mining Software Repositories (MSR) community has benefited enormously from widely shared data sets.  Such data sets document the canonical problems in a field.
They serve to cluster together like-minded researchers while also
  allowing   them to generate reproducible results. Further, they can be used by
   newcomers to learn state-of-the-set methods in this field. Finally, they enable the mainstay of good science:
reputable, repeatable,  improvable, and even refutable results.

@@

A problem with this kind of trade-off is that it must explore some
underlying space of options.  In a conventional approach, some
business process model could be developed, then exercised many
times. Such a {\em data farming} approach: \be
\item
{\em Plants a seed.} Build a model from domain information. All uncertainties or missing parts of the domain information are modeled as a space of possibilities.
\item {\em Grows the data.} Execute model and, when the model moves into the space of possibilities, output is created by selecting at random from the possibilities.
\item {\em Harvests.} Summarize the grown data via data mining.
\item Optionally, use the harvested summaries to improve the model;
  then, go to 1. \ee

\begin{figure}[!b]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
Let $\{A,B,C,D\}$ denote the
true negatives,
false negatives,
false positives, and
true positives
(respectively) found by a software defect detector.
Also, let $L_A L_b, L_c, L_d$ be the lines of code
seen in the parts of system that fall
into $A,B,C,D$. Then:
\[
\begin{array}{r@{~}l}
pd=recall=&D / (B+D)\\
pf=&C / (A+C)\\
prec=precision=&D / (D+C)\\
acc=accuracy=&(A+D) / (A+B+C+D)\\
support=&(C+D) / (A+B+C+D)\\
\textit{effort}=&(L_c+L_d) / (L_a + L_b + L_c + L_d)\\
reward=&pd / \textit{effort}
\end{array}
\]\\\hline
\end{tabular}
\caption{Some assessment criteria for defect predictors.}\label{fig:criteria}
\end{figure}

\begin{figure}[!t]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
Some goals relate to aspects of defect prediction:
\begin{enumerate}
\item
Mission-critical systems are risk averse and may accept very high false alarm rates,
just as long as they catch any life-threatening possibility. That is, such projects
do not care about effort- they want to {\em maximize recall} regardless of any impact
that might have on the false alarm rate.
\item
Cost averse managers may accept lower probabilities of
detection (the recall measure), just as long as they {\em do not waste budgets on false alarms}. This community
seeks to {\em minimize false alarms} while maintaining {\em some level of adequate recall}.
\item  Suppose a new hire wants
 to impress their manager. That
 new hire might want to ensure that no result presented to  management contains  true negative;
i.e. they wish to {\em maximize precision}.
\item
Some communities do not care about   low precision,
just as long as a small fraction the data is returned. Hayes, Dekhytar, \& Sundaram call this fraction
{\em selectivity} and offer an
extensive discussion of the merits of this measure~\cite{hayes06}.
\end{enumerate}\\\hline
Beyond defect prediction are other goals that combine defect prediction with other economic
factors:
\begin{enumerate}
\setcounter{enumi}{4}
\item
Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
that contain the most bugs.
\item In other work, Lumpe et al. are concerned about
 {\em amateur  bug fixes}; i.e. those that made by programmers to
regions of the code that are unfamiliar, to them~\cite{me11f}.
Such amateur fixes are highly correlated to errors and, hence, to
avoid such incorrect bug fixes, we have to optimize
for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
\item In {\em Better-faster-cheaper}, we seek  project changes that lead
to fewer defects and faster development times using less resources~\cite{elrawas10,me07f,me09a,me09f}.
\item {\em  Rush-to-market} is another economic-based optimization measure.
A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
used to subsequently fix any issues with version 1.0)~\cite{huang06}.
\item
With Sayyad~\cite{sayyad13a,sayyad13b}, we have explored models of software product
lines whose value propositions are five-fold:
(1)~offer feature rich products (i.e. that
use as {\em many features} as possible);
(2)~selecting from features with {\em fewest past defects};
favoring those that we have (3)~{\em used before}; and which
(4)~{\em cost
least} to adopt; all the while (5)~avoiding {\em any violations} of
required properties of these
products.
\end{enumerate}
\\\hline
All the above measures relate to the tendency of a predictor to find something. Another style
of measure would be to check the {\em variability} of that predictor.
\begin{enumerate}
\setcounter{enumi}{8}
\item
In their study on reproducibility of SE results,
 Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{mockus09}.
\end{enumerate}\\\hline
\end{tabular}
\caption[Different users value different things.]{Different users value different things.
Note that some of
these goals are defined in terms of
\fig{criteria}.
}\label{fig:goals}
\end{figure}

>>>>

\usepackage{color}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{graphicx} 
\usepackage{multirow}
\usepackage{siunitx}
\usepackage{rotating}
\usepackage{eqparbox}
\usepackage{wrapfig}
\usepackage{mathtools}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{lstlinebgrd}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hhline}

@@

%Conference
\acmConference[MSR'18]{Sweden}{May 2018}{} 
\acmYear{2018}
\copyrightyear{2018}

@@

\maketitle
\pagestyle{plain}
% \input{samplebody-conf}
\section{Introduction}
The Mining Software Repositories (MSR) community has benefited enormously from widely shared data sets.  Such data sets document the canonical problems in a field.
They serve to cluster together like-minded researchers while also
  allowing   them to generate reproducible results. Further, they can be used by
   newcomers to learn state-of-the-set methods in this field. Finally, they enable the mainstay of good science:
reputable, repeatable,  improvable, and even refutable results.

@@

A problem with this kind of trade-off is that it must explore some
underlying space of options.  In a conventional approach, some
business process model could be developed, then exercised many
times. Such a {\em data farming} approach: 
\begin{itemize}
\item
{\em Plants a seed.} Build a model from domain information. All uncertainties or missing parts of the domain information are modeled as a space of possibilities.
\item {\em Grows the data.} Execute model and, when the model moves into the space of possibilities, output is created by selecting at random from the possibilities.
\item {\em Harvests.} Summarize the grown data via data mining.
\item Optionally, use the harvested summaries to improve the model;
  then, go to 1. 
\end{itemize}

  While these two terms have many differences, they relate to a similar concept:
\begin{enumerate}
\item Tuning instability refers to uncertainties inside a model;
\item Value variability refers to uncertainty on how to assess the outputs of a model.
\end{enumerate}
Our reading of the software engineering literature is that most papers only explore
a small subset of Figure 23.1 or Figure 23.2. We think this is a mistake and researchers
should more to a more general framework where they explore a wide and changing set
of evaluation criteria. The next section describes one such framework.
23.2.2.3 Exploring Instability and Variability
To address the above problems, we adopt two strategies:
\begin{itemize}
\item  To address value variability we:
\begin{itemize}
    \item Use tools that allow for the customization of the value proposition used to
    guide the search.
    \item Then run the models using different value propositions.
\end{itemize}
\item To address tuning instability we:
\begin{itemize}
    \item Determine the space of known tunings for a model;
    \item Allow models to range over that space;
    \item Extensively simulate the models;
    \item Look for stable conclusions over the entire space of tunings.
\end{itemize}
\end{itemize}
The rest of this chapter offers an example of this kind of analysis

\begin{figure}[!b]
\small
\begin{tabular}{p{.95\linewidth}}\hline
\rowcolor{gray!10}
Let $\{A,B,C,D\}$ denote the
true negatives,
false negatives,
false positives, and
true positives
(respectively) found by a software defect detector.
Also, let $L_A L_b, L_c, L_d$ be the lines of code
seen in the parts of system that fall
into $A,B,C,D$. Then:
\[
\begin{array}{r@{~}l}
\mathit{pd}=\mathit{recall}=&D / (B+D)\\
\mathit{pf}=&C / (A+C)\\
\mathit{prec}=\mathit{precision}=&D / (D+C)\\
\mathit{acc}=\mathit{accuracy}=&(A+D) / (A+B+C+D)\\
\mathit{support}=&(C+D) / (A+B+C+D)\\
\textit{effort}=&(L_c+L_d) / (L_a + L_b + L_c + L_d)\\
\mathit{reward}=&\mathit{pd} / \textit{effort}
\end{array}
\]\\\hline
\end{tabular}
\caption{Some assessment criteria widely used in MSR.}\label{fig:criteria}
\end{figure}

\begin{figure}[!t]
\small

\begin{tabular}{p{.95\linewidth}}\hline 
\rowcolor{gray!10}
Some goals relate to aspects of defect prediction:
\begin{enumerate}[leftmargin=0.4cm]

\item
Mission-critical systems are risk averse and may accept very high false alarm rates,
just as long as they catch any life-threatening possibility. That is, such projects
do not care about effort- they want to {\em maximize recall} regardless of any impact
that might have on the false alarm rate.
\item
Cost averse managers may accept lower probabilities of
detection (the recall measure), just as long as they {\em do not waste budgets on false alarms}. This community
seeks to {\em minimize false alarms} while maintaining {\em some level of adequate recall}.
\item  Suppose a new hire wants
 to impress their manager. That
 new hire might want to ensure that no result presented to  management contains  true negative;
i.e. they wish to {\em maximize precision}.
\item
Some communities do not care about   low precision,
just as long as a small fraction the data is returned. Hayes, Dekhytar, \& Sundaram call this fraction
{\em selectivity} and offer an
extensive discussion of the merits of this measure~\cite{hayes06}.
\end{enumerate}
\\ \hline
Beyond defect prediction are other goals that combine defect prediction with other economic
factors:
\begin{enumerate}[leftmargin=0.4cm]
\setcounter{enumi}{5}
\item
Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
that contain the most bugs.
\item In other work, Lumpe et al. are concerned about
 {\em amateur  bug fixes}; i.e. those that made by programmers to
regions of the code that are unfamiliar, to them~\cite{me11f}.
Such amateur fixes are highly correlated to errors and, hence, to
avoid such incorrect bug fixes, we have to optimize
for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
\item In our  {\em better-faster-cheaper} work, we seek  project changes that lead
to fewer defects and faster development times using less resources~\cite{elrawas10,me07f,me09a,me09f}.
\item {\em  Rush-to-market} is another economic-based optimization measure.
A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
used to subsequently fix any issues with version 1.0)~\cite{huang06}.
\item
With Sayyad~\cite{sayyad13a,sayyad13b}, we have explored models of software product
lines whose value propositions are five-fold:
(1)~offer feature rich products (i.e. that
use as {\em many features} as possible);
(2)~selecting from features with {\em fewest past defects};
favoring those that we have (3)~{\em used before}; and which
(4)~{\em cost
least} to adopt; all the while (5)~avoiding {\em any violations} of
required properties of these
products.
\end{enumerate}
\\ \hline
All the above measures relate to the tendency of a predictor to find something. Another style
of measure would be to check the {\em variability} of that predictor.
\begin{enumerate}[leftmargin=0.4cm]
\setcounter{enumi}{8}
\item
In their study on reproducibility of SE results,
 Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{mockus09}.
\end{enumerate}\\\hline
\end{tabular}
\caption[Different users value different things.]{Different users value different things.
Technical note:  some of
these goals are defined in terms of
Figure~\ref{fig:criteria}.
}\label{fig:goals}
\end{figure}

XXX defterming goals actaully part of the modeling process. e.g softwaregoals.
